Figures

### 2020-04-14 manuscript/figures.Rmd
fix figure numbering
show proxy measures on diagram

![Diagram showing the assumption of most lake depth models that the nearshore slope extends into the lake and that all lakes have a common relationship between nearshore and inlake slope. ](../figures/slope_diagram.pdf){width=75%}

@@

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r 01_predictors, fig.cap = "Table 1: Summary of lake depth predictor variables for modelling efforts (and for lakes continent-wide).", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../tables/01_predictors.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{3}

>>>>

![Diagram showing the relations between true (black) and proxy (orange) metrics of lake geometry. Calculated depth from Equation 1 requires a distance and a slope metric.](../figures/slope_diagram_new.pdf){width=75%}

@@

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r 01_predictors, fig.cap = "Table 1: Summary of lake depth predictor variables for modelling efforts (and for lakes continent-wide).", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../tables/01_predictors.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{2}
